---
title: "Exploring categorisation of prime and composite quantities in honeybees using perceptual grouping"
author: "Leslie Ng and Scarlett Howard"
date: "04-07-2023"
output:
  html_document:
   toc: yes
   toc_float: yes
   collapsed: true 
   smooth_scroll: true
   depth: 3 
   highlight: tango # different theme for the appearance of the code
   theme: flatly
   code_folding: hide
self_contained: yes
mode: selfcontained
editor_options:
  chunk_output_type: console
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../Output") })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r, echo=FALSE}
knitr::opts_chunk$set(error = TRUE)
```


# **Introduction**


In this document we tested if free-flying honey bees that are habituated to even composite numbers spontaneously discriminate an odd prime number from an odd composite number. This document provides details on data processing, statistical analysis and figures of the original manuscript submitted for peer review (titled: "xxx").

The following code is written in the R programming language.


EE = Equal element size condition, 
SA = Equal surface area condition


# **Libraries** 

### *Install packages*
```{r eval=FALSE}
install.packages("lme4")  # For fitting models
install.packages("ggplot2") # For plotting
install.packages("wesanderson") # Color palette
install.packages("dplyr") # Data processing
install.packages("tidyverse") # QoL
install.packages("ggpubr") # Create figure
install.packages("patchwork") # Create figure
```

### *Load packages*

```{r, message=FALSE, warning=FALSE}
library(lme4) 
library(ggplot2) 
library(wesanderson)
library(dplyr) 
library(tidyverse) 
library(patchwork) 
```



# **Data importing**

```{r, message=FALSE, results="hide"}

PRIMEDATA <- read.csv("../Data/prime_data.csv", header=TRUE)

PRIMEGRP <- read.csv(
  "../Data/primegrouped_data.csv", header=TRUE)

CONTROL <- read.csv(
  "../Data/control_data.csv", header=TRUE)

#Subset Prime data 

PRIMEDATA$BEEID <- as.factor(PRIMEDATA$BEEID) # Treat Bee ID as factor
POSITIVE <- subset(PRIMEDATA, CONDITION == "POSITIVE") 
NEGATIVE <- subset(PRIMEDATA, CONDITION == "NEGATIVE") 
POS7v9 <-subset(POSITIVE, TEST == "7v9") 
POS11v9 <-subset(POSITIVE, TEST == "11v9") 
POS13v15 <-subset(POSITIVE, TEST == "13v15") 
NEG7v9 <-subset(NEGATIVE, TEST == "7v9") 
NEG11v9 <-subset(NEGATIVE, TEST == "11v9") 
NEG13v15 <-subset(NEGATIVE, TEST == "13v15") 
summary(POS7v9)
summary(NEG7v9)
summary(POS11v9)
summary(NEG11v9)
summary(POS13v15)
summary(NEG13v15)

#Subset Prime grouped data

PRIMEGRP$BEEID <- as.factor(PRIMEGRP$BEEID) # Treat Bee ID as factor
POSITIVE_GRP <- subset(PRIMEGRP, CONDITION == "POS") 
NEGATIVE_GRP <- subset(PRIMEGRP, CONDITION == "NEG") 
POS7v9_GRP <-subset(POSITIVE_GRP, TEST == "7v9") 
POS11v9_GRP <-subset(POSITIVE_GRP, TEST == "11v9") 
POS13v15_GRP <-subset(POSITIVE_GRP, TEST == "13v15") 
NEG7v9_GRP <-subset(NEGATIVE_GRP, TEST == "7v9") 
NEG11v9_GRP <-subset(NEGATIVE_GRP, TEST == "11v9") 
NEG13v15_GRP <-subset(NEGATIVE_GRP, TEST == "13v15") 
POSCONT_GRP <-subset(POSITIVE_GRP, TEST == "control")
NEGCONT_GRP<-subset(NEGATIVE_GRP, TEST == "control")
summary(POS7v9_GRP)
summary(NEG7v9_GRP)
summary(POS11v9_GRP)
summary(NEG11v9_GRP)
summary(POS13v15_GRP)
summary(NEG13v15_GRP)

#Subset control data

CONTROL$BEEID <- as.factor(CONTROL$BEEID) # Treat Bee ID as factor

conSA <-subset(CONTROL, CONDITION == "SA") 
conEE <-subset(CONTROL, CONDITION == "EE") 

EEcon3v1 <-subset(conEE, TEST == "3v1") 
EEcon3v2 <-subset(conEE, TEST == "3v2") 
EEcon3v4 <-subset(conEE, TEST == "3v4") 
EEcon3v5 <-subset(conEE, TEST == "3v5") 

SAcon3v1 <-subset(conSA, TEST == "3v1") 
SAcon3v2 <-subset(conSA, TEST == "3v2") 
SAcon3v4 <-subset(conSA, TEST == "3v4") 
SAcon3v5 <-subset(conSA, TEST == "3v5") 

summary(EEcon3v1)
summary(EEcon3v2)
summary(EEcon3v4)
summary(EEcon3v5)
summary(SAcon3v1)
summary(SAcon3v2)
summary(SAcon3v4)
summary(SAcon3v5)


```

# **Generalized linear models**

## Experiment 1

```{r message=FALSE, results='hide', error=FALSE}

lm1 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = POS7v9) 
summary(lm1)
lm2 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = POS11v9) 
summary(lm2)
lm3 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = POS13v15) 
summary(lm3)
lm4 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = NEG7v9) 
summary(lm4)
lm5 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = NEG11v9) 
summary(lm5)
lm6 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = NEG13v15) 
summary(lm6)

```

### *Pooled dataset* 

We use and report models using a pooled dataset (combining equal element size and equal surface area groups) as we found no statistically significant results in either condition

```{r message=FALSE, error=FALSE}
 
EXP1POOLED7v9 <-subset(PRIMEDATA, TEST == "7v9") 
EXP1POOLED11v9 <-subset(PRIMEDATA, TEST == "11v9") 
EXP1POOLED13v15 <-subset(PRIMEDATA, TEST == "13v15") 

lm7 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = EXP1POOLED7v9) 
summary(lm7)
lm8 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = EXP1POOLED11v9) 
summary(lm8)
lm9 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = EXP1POOLED13v15) 
summary(lm9)

```


### *Confidence intervals*

```{r results='hide', message=FALSE, error=FALSE, warning=FALSE}

confint(lm7)
EXP1_7v9confintlow <-(exp(-0.3941168)/(1 + exp( -0.3941168)))
EXP1_7v9confinthigh <-(exp(0.5825354)/(1 + exp(0.5825354)))
confint(lm8)
EXP1_11v9confintlow <-(exp(-0.1001439)/(1 + exp(-0.1001439)))
EXP1_11v9confinthigh <-(exp(0.5160843)/(1 + exp(0.5160843)))
confint(lm9)
EXP1_13v15confintlow <-(exp(-0.3178457)/(1 + exp(-0.3178457)))
EXP1_13v15confinthigh <-(exp(0.2373101)/(1 + exp(0.2373101)))

```

## Experiment 2

```{r results='hide', error=FALSE, message=FALSE}

lm10 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = POS7v9_GRP) 
summary(lm10)
lm11 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = POS11v9_GRP) 
summary(lm11)
lm12 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = POS13v15_GRP) 
summary(lm12)
lm13 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = POSCONT_GRP) 
summary(lm13)

lm14 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = NEG7v9_GRP) 
summary(lm14)
lm15 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = NEG11v9_GRP) 
summary(lm15)
lm16 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = NEG13v15_GRP) 
summary(lm16)
lm17 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = NEGCONT_GRP) 
summary(lm17)

```

### *Pooled dataset*

We use and report models using a pooled dataset (combining equal element size and equal surface area groups) as we found no statistically significant results in either condition

```{r message=FALSE, error=FALSE}

EXP2POOLED7v9 <-subset(PRIMEGRP, TEST == "7v9") 
EXP2POOLED11v9 <-subset(PRIMEGRP, TEST == "11v9") 
EXP2POOLED13v15 <-subset(PRIMEGRP, TEST == "13v15") 
EXP2POOLEDNEGCONT <-subset(PRIMEGRP, TEST == "control") 

lm18 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = EXP2POOLED7v9) 
summary(lm18)
lm19 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = EXP2POOLED11v9) 
summary(lm19)
lm20 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = EXP2POOLED13v15) 
summary(lm20)
lm21<-glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = EXP2POOLEDNEGCONT) 
summary(lm21)

```


### *Confidence intervals*

```{r results='hide', error=FALSE, warning=FALSE, message=FALSE}

confint(lm18)
EXP2_7v9confintlow <-(exp(-0.04782218)/(1 + exp(-0.04782218)))
EXP2_7v9confinthigh <-(exp(0.5434547)/(1 + exp(0.5434547)))
confint(lm19)
EXP2_11v9confintlow <-(exp(-0.197514)/(1 + exp(-0.197514)))
EXP2_11v9confinthigh <-(exp(0.3590998)/(1 + exp(0.3590998)))
confint(lm20)
EXP2_13v15confintlow <-(exp(-0.4808859)/(1 + exp(-0.4808859)))
EXP2_13v15confinthigh <-(exp(0.07708543)/(1 + exp(0.07708543)))
confint(lm21)
EXP2_NEGCONTconfintlow <-(exp(-0.3787003)/(1 + exp(-0.3787003)))
EXP2_NEGCONTconfinthigh <-(exp(0.1772473)/(1 + exp(0.1772473)))

```

## Control experiment

```{r message=FALSE, error=FALSE}

clm1 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = EEcon3v1) 
summary(clm1)
clm2 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = EEcon3v2) 
summary(clm2)
clm3 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = EEcon3v4) 
summary(clm3)
clm4 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = EEcon3v5) 
summary(clm4)
clm5 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = SAcon3v1) 
summary(clm5)
clm6 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = SAcon3v2) 
summary(clm6)
clm7 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = SAcon3v4) 
summary(clm7)
clm8 <- glmer(CHOICE~ 1 + (1|BEEID), family = binomial, data = SAcon3v5) 
summary(clm8)


```

### *Confidence intervals*


```{r results='hide', error=FALSE, message=FALSE, warning=FALSE}

confint(clm1)
EE3v1confintlow <-(exp(0.3592665)/(1 + exp(0.3592665)))
EE3v1confinthigh <-(exp(1.2555766)/(1 + exp(1.2555766)))
confint(clm2)
EE3v2confintlow <-(exp(-0.632105)/(1 + exp(-0.632105)))
EE3v2confinthigh <-(exp(0.6466399)/(1 + exp(0.6466399)))
confint(clm3)
EE3v4confintlow <-(exp(-0.408491)/(1 + exp(-0.408491)))
EE3v4confinthigh <-(exp(0.5026474)/(1 + exp(0.5026474)))
confint(clm4)
EE3v5confintlow <-(exp(-0.3296674)/(1 + exp(-0.3296674)))
EE3v5confinthigh <-(exp(0.7213893)/(1 + exp(0.7213893)))

confint(clm5)
SA3v1confintlow <-(exp(-0.1827046)/(1 + exp(-0.1827046)))
SA3v1confinthigh <-(exp(0.7875859)/(1 + exp(0.7875859)))
confint(clm6)
SA3v2confintlow <-(exp(-0.6834336)/(1 + exp(-0.6834336)))
SA3v2confinthigh <-(exp(0.7978965)/(1 + exp(0.7978965)))
confint(clm7)
SA3v4confintlow <-(exp(-0.2441276)/(1 + exp(-0.2441276)))
SA3v4confinthigh <-(exp(0.5751515)/(1 + exp(0.5751515)))
confint(clm8)
SA3v5confintlow <-(exp(-0.6521079)/(1 + exp(-0.6521079)))
SA3v5confinthigh <-(exp(0.3092899)/(1 + exp(0.3092899)))
```


# **Figures**

```{r message=FALSE, results='hide', error=FALSE}

# Create dataframe for experiment 1 bargraph

dframe <- data.frame(Test = rep(c("7v9", "11v9", "13v15")),
                     proportion = c(0.52,0.55,0.49),
                     confintlow = c(EXP1_7v9confintlow,EXP1_11v9confintlow,EXP1_13v15confintlow),
                     confinthigh = c(EXP1_7v9confinthigh,EXP1_11v9confinthigh,EXP1_13v15confinthigh))


exp1points <- PRIMEDATA %>%   # calculate mean of each block for each bee
  group_by(BEEID, TEST, CONDITION) %>% 
  summarize(prop = mean(CHOICE)) 


# Create dataframe for experiment 2 bargraph

dframe2 <- data.frame(Test = rep(c("7v9", "11v9", "13v15","control")), 
                     proportion = c(0.56,0.52,0.45,0.475),
                     confintlow = c(EXP2_7v9confintlow,EXP2_11v9confintlow,EXP2_13v15confintlow,EXP2_NEGCONTconfintlow),
                     confinthigh = c(EXP2_7v9confinthigh,EXP2_11v9confinthigh,EXP2_13v15confinthigh,EXP2_NEGCONTconfinthigh))

exp2points <- PRIMEGRP %>%   # calculate mean of each block for each bee
  group_by(BEEID, TEST, CONDITION) %>% 
  summarize(prop = mean(CHOICE))


# Create dataframe for control experiment bargraph

dframecon <- data.frame(Test = rep(c("3v1", "3v2","3v4","3v5"), each = 2), 
                    Condition = rep(c("EE", "SA"), times = 4),
                    proportion = c(0.6889, 0.57, 0.5, 0.51, 0.5111, 0.54, 0.5444, 0.46),
                     confintlow = c(EE3v1confintlow, SA3v1confintlow, EE3v2confintlow, SA3v2confintlow, EE3v4confintlow, SA3v4confintlow, EE3v5confintlow, SA3v5confintlow),
                     confinthigh = c(EE3v1confinthigh, SA3v1confinthigh, EE3v2confinthigh, SA3v2confinthigh, EE3v4confinthigh, SA3v4confinthigh, EE3v5confinthigh, SA3v5confinthigh))


controlpoints <- CONTROL %>%   # calculate mean of each block for each bee
  group_by(BEEID, TEST, CONDITION) %>% 
  summarize(prop = mean(CHOICE)) 

              
# Generate bargraph for experiment 1 

exp1graph <- ggplot()+
  labs (x= "Condition", y = "Mean proportion of correct choices") +
  geom_bar(data = dframe, aes(x = Test, y = proportion, fill = Test), stat = "identity", position = "dodge") + 
   geom_point(data = exp1points, aes(x = TEST, y = prop), position = position_jitter(width=0.1), size =0.7, colour="dark grey") +
  geom_errorbar(data= dframe, aes(x = Test, y = proportion, ymin = confintlow, ymax = confinthigh), width=.2, position=position_dodge(.9)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", colour = " black") +
  scale_fill_manual(values = wes_palette("GrandBudapest2", n = 3)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1, suffix = NULL)) +
  scale_x_discrete(labels=c("7v9" = "7 vs 9", "11v9" = "11 vs 9", "13v15" = "13 vs 15"))+
  theme(panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        aspect.ratio = 1/1, 
        axis.title.y = element_text(vjust = 5),
        axis.title.x = element_text(vjust = -3))

# Generate bargraph for experiment 2

exp2graph <- ggplot()+
  labs (x= "Condition", y = "Mean proportion of correct choices") +
  geom_bar(data = dframe2, aes(x = Test, y = proportion, fill = Test), stat = "identity", position = "dodge") + 
   geom_point(data = exp2points, aes(x = TEST, y = prop), position = position_jitter(width=0.1), size =0.7, colour="dark grey") +
  geom_errorbar(data= dframe2, aes(x = Test, y = proportion, ymin = confintlow, ymax = confinthigh), width=.2, position=position_dodge(.9)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", colour = " black") +
  scale_fill_manual(values = wes_palette("GrandBudapest2", n = 4)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1, suffix = NULL)) +
  scale_x_discrete(labels=c("7v9" = "7 vs 9", "11v9" = "11 vs 9", "13v15" = "13 vs 15", "control" = "control"))+
  theme(panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        aspect.ratio = 1/1, 
        axis.title.y = element_text(vjust = 5),
        axis.title.x = element_text(vjust = -3))

# Generate bargraph for control experiment

congraph <- ggplot()+
  labs (x= "Condition", y = "Mean proportion of correct choices") +
  geom_bar(data = dframecon, aes(x = Test, y = proportion, fill = Condition), stat = "identity", position = "dodge") + 
  geom_hline(yintercept = 0.5, linetype = "dashed", colour = " black") +
  geom_point(data = controlpoints, aes(x = TEST, y = prop, fill = CONDITION), position = position_jitterdodge(jitter.width=0.2, jitter.height = 0.01, dodge.width = 0.9),       show.legend = FALSE, size =0.5, colour="dark grey") +
  scale_fill_manual(values = wes_palette("GrandBudapest2", n = 2)) +
  geom_errorbar(data= dframecon, aes(x = Test, y = proportion, ymin = confintlow, ymax = confinthigh, group = Condition), width=.15, position=position_dodge(.9)) +
  geom_text(data= dframecon, x =0.775, y = 0.82, label ="*", size =6) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1, suffix = NULL))+
  theme(panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        aspect.ratio = 1/1,
        plot.margin = margin(0.3,0.3,0.1,0.4, "cm"))

```

## Generate Figure x

```{r message=FALSE}
figx <- exp1graph + exp2graph
figx
ggsave("figx.pdf", device = pdf, height= 4, width=10, dpi = 300, path = "Output")
congraph
ggsave("figx2.pdf", device = pdf, height= 5, width=6, dpi = 300, path = "Output")
```


```{r eval=FALSE}
figx + plot_annotation(tag_levels = "A")
ggsave("figx.pdf", device = pdf, height= 4, width=10, dpi = 300, path = "Output")
ggsave("figx.png", device = png, height= 4, width=10, dpi = 300, path = "Output")
congraph
ggsave("figx2.pdf", device = pdf, height= 5, width=6, dpi = 300, path = "Output")
ggsave("figx2.png", device = png, height= 5, width=6, dpi = 300, path = "Output")

```

